TBD

### 2016-10-14 paper.tex
started to clean up normal equation

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of only one major outer loop. It turns out that in the worst possible case 
the number of major iterations that is required by CG to converge is proportional to $\sqrt{\kappa}$.

The computational complexity of CG is $\mathbb{O}(\sqrt{\kappa}m)$, where $\kappa$ is the generalized specctral condition number of the matrix $\bA$ and $m$ is the number of
non-zero entries in the matrix $\bA$. The mathematical
definition of $\kappa(\bA)$ is
\begin{equation}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda^{+}_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ denotes the largest eigenvalue of $\bA$ and $\lambda^{+}_{\textrm{min}}$ presents the smallest positive eigenvalue. 
Interpreting the computational complexity equation further. Note from Algorithm 1 that the CG method has one major outer loop. In the worst possible case, the amount of iterations needed to converge is
proportional to $\sqrt{\kappa}$. Also notice that the most expensive 
operation that is conducted within each loop is the vector-matrix product, which has complexity $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in the matrix.
The computational complexity of the CG method is therefore 
\begin{equation}
\mathbb{O}(\sqrt{\kappa}m) 
\end{equation}

It should now be clear to
the reader why the CG method is espicially applicable to sparse linear systems, since in those cases $m < N^2$. 
We can improve the computational complexity of the CG method by preconditioning. 
[Preconditioning is a technique for improving the condition number of a matrix. Suppose that ' is a
symmetric, positive-definite matrix that approximates, but is easier to invert. We can solve indirectly by solving] - RW directly coppied from source
\begin{equation}
\bM^{-1}\bA\bx = \bM^{-1}\bb
\end{equation}

The best precondtioner would be the preconditioner which makes $\kappa$ unity, i.e. completly
eliminating it from the computational complexity equation. The only choice of $\bM$ which is capable of best way to do this is to chooose as preconditioner the matrix $(\bA)^{-1}$, which is what we would like to determine in the frist place.
If the diagonal entries of $\bA$ are more significant than its off-diagonal entries, then the Jacobian preconditioner is a good preconditioner to use. 
State better that the choice of preconditioner, the value of kappa and what the effect of this would be on the computational complexity of the method.

In general, when $\bA$ has dimensions $m\times n$, with $m > n$ we can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bA^H\bA\bx = \bA^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bA\bx\|. 
\end{equation}
If $\bA^H\bA$ is invertiable then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bA^H\bA$ is singular there are an infinite amount of solutions
that minimizes Eq.~\eqref{eq:norm_ls}. Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}

>>>>

\subsection{Computational Complexity}
\citet{Kaniel1966} was able to determine convergence bounds for CG using Chebyshev polynomials. A much more in depth analysis of CG convergence can be found in
\citep{Sluis1986}. As can be seen from Algorithm \ref{algo:CG}, the CG method makes use of a major outer loop (line 6 of Algorithm \ref{algo:CG}). It turns out that at worst 
the number of major iterations that CG requires to converge\footnote{If the $\bA$-norm is used to calculate the error.} is proportional to $\sqrt{\kappa}$, where $\kappa$ is the specctral condition number of the matrix $\bA$.
The mathematical definition of $\kappa(\bA)$ is
\begin{equation}
\label{eq:kappa}
\kappa(\bA) = \frac{\lambda_{\textrm{max}}}{\lambda_{\textrm{min}}}, 
\end{equation}
where $\lambda_{\textrm{max}}$ and $\lambda_{\textrm{min}}$ respectively denote the largest and the smallest eigenvalue of $\bA$.
Moreover, the most expensive operation that is conducted within each major loop of Algorithm~\ref{algo:CG} is the vector-matrix product $\bA\bp$, which has a complexity of $\mathbb{O}(m)$, where $m$ is the number of non-zero entries in $\bA$.
The computational complexity of CG is therefore 
\begin{equation}
\label{eq:cg_bound}
\mathbb{O}(\sqrt{\kappa}m). 
\end{equation}
It should now also be clear to the reader why the CG method is especially applicable to sparse linear systems, since in those cases $m < P^2$.

\subsection{Preconditioning}
Preconditioning is a technique which allows us to improve the condition number of a matrix. Let $\bM$ be a positive-definite Hermitian matrix.
We can now indirectly solve for $\bx$ by using 
\begin{equation}
\label{eq:prec}
\bM^{-1}\bA\bx = \bM^{-1}\bb.
\end{equation}
If $\bM$ is a good preconditioner then $\kappa(\bM^{-1}\bA) \ll \kappa(\bA)$, i.e. a good preconditioner lowers the condition number of a matrix which in turn increases the convergence speed 
of CG (see Eq.~\eqref{eq:cg_bound}). The best possible choice of $\bM$ would therefore be $\bA$, which would lead to $\kappa$ (as the largest and smallest eigenvalue of the Identity matrix is equal to one) becoming unity.
If $\kappa$ is one then Eq.~\eqref{eq:cg_bound} simplifies and becomes $\mathbb{O}(m)$. However, if we knew the inverse of $\bA$ then obtaining $\bx$ would be trivial and there would be no need for the CG method in the first place. 
In short, a good preconditioner $\bM$ must approximate $\bA$ fairly accurately. However, if it is not much less expensive to 
compute the inverse of $\bM$ than that of $\bA$ we actually gain nothing (see Eq.~\eqref{eq:prec}).

If the diagonal entries of $\bA$ is much more significant than its off-diagonal entries then the 
Jacobian preconditioner is a good choice of $\bM$. The Jacobian preconditioner is computed as follows:
\begin{equation}
\bM = \bA\odot\bI, 
\end{equation}
where $\bI$ is the identity matrix. Since the Jacobian preconditioner is a diagonal matrix its inverse can be obtained trivially.

\subsection{Normal Equation}
Lets assume that instead of Eq.~\eqref{eq:linear_system} we have a more general linear system, i.e.
\begin{equation}
 \bb = \bB\bx,
\end{equation}
where $\bb\in\mathbb{C}^K$, $\bx\in\mathbb{C}^P$  and $\bB\in\mathbb{C}^{K \times P}$, with $K > P$. We can use the normal equation 
\begin{equation}
\label{eq:normal_equation}
\bB^H\bB\bx = \bB^H\bb 
\end{equation}
to estimate the $\bx$ that minimizes
\begin{equation}
\label{eq:norm_ls}
\|\bb-\bB\bx\|_F^2. 
\end{equation}
There are a few important observations that we can make while inspecting Eq.~\eqref{eq:normal_equation}:
\begin{enumerate}
\item $\bB^H\bB$ is an Hermitian positive semi-definite square matrix by construction.
\item $\bB^H\bb$ is in the column range of $\bB^H\bB$; this follows trivially from 
\begin{equation}
\bB^H\bb \in \mathcal{R}(\bB^H) \implies \bB^H\bb \in \mathcal{R}(\bB^H\bB).   
\end{equation}
\end{enumerate}

Recall that we mentioned that in general we can only solve Eq.~\eqref{eq:linear_system} with CG if $\bA$ is an Hermitian positive-definite square matrix. Recently,
\citet{Lu2015} showed that the CG method has an even broader applicability, it can be used to solve Eq.~\eqref{eq:linear_system} even if $\bA$ is an Hermitian positive semi-definite
square Hermitian matrix as long as $\bb$ is in the column range of $\bA$. Combining the result from Lu with the aformentioned two observations we made in regards to Eq.~\eqref{}

It now trivially follows \citet{Lu2015} from follows that we can apply the CG method to solve any normal equation. We have already

%It is a well known fact that the normal equation has at least one solution. If $\bB^H\bB$ is invertible then the solution that minimizes Eq.~\eqref{eq:norm_ls} is unique. In contrast, if $\bB^H\bB$ is singular there are an infinite amount of solutions
%that minimizes Eq.~\eqref{eq:norm_ls}. 
%Interestingly enough, we can use the CG method to solve Eq.~\eqref{eq:normal_equation} in either one of the previously mentioned scenarios.

Moreover, we can use the CG method to solve Eq.~\eqref{eq:normal_equation}, since $\bA^H\bA$ is Hermitian by construction 
and $\bA^H\bb$ is in the column range of $\bA^H\bA$.
\begin{equation}
\bA^H\bb \in \mathcal{R}(\bA^H) \implies \bA^H\bb \in \mathcal{R}(\bA^H\bA).   
\end{equation}
